\documentclass{article}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{pgfplots}
\usepackage{amsfonts}
\usepackage[margin=2.5cm]{geometry}
\usepackage{graphicx}
\usepackage[export]{adjustbox}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{lastpage}
\usepackage{mathtools}

\pagestyle{fancy}
\fancyhf{}

\pgfplotsset{compat = 1.18}

\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

\rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}}

\newcommand\SLash{\char`\\}
\newtheorem*{def*}{Definition}
\newtheorem*{theo*}{Theorem}

\title{CANTOR SETS AND SEQUENCE SPACES}
\author{Renan Wenzel}
\date{\today}

\begin{document}
\maketitle
\tableofcontents
\newpage
\section{Preliminaries(Done during lectures)}

\paragraph{} This first part is to recall and introduce a few ideas needed to grasp the content within these notes.

\begin{def*}
  A topology $\tau$ on X is a collection of sets such that
\end{def*}
\begin{itemize}
  \item[i)] $X, \emptyset\in{\tau}$
  \item[ii)] $\text{ If } U _{1}, \cdots, U _{\alpha} \text{ are an arbitrary family of sets } U _{\alpha}\in{\tau}, 
  \alpha\in{J}, \text{ then } \bigcup _{\alpha\in{J}}U _{\alpha}\in{\tau}$
  \item[iii)] $\text{ If } U _{1}, \cdots, U _{n} \text{ belong to } \tau, \text{ then } \bigcap _{i=1}^{n}U _{i}\in{\tau}.$
\end{itemize}

\begin{def*}
  The discrete topology on X is the one in which open sets are subsets of X.
\end{def*}

\begin{def*}
  A metric on a set X is a function $d:X\times{X}\rightarrow \mathbb{R}$ which satisfies the following
\end{def*}
\begin{itemize}
  \item[i)] $d(x, y)\geq{0}, d(x, y) = 0\Longleftrightarrow x = y;$
  \item[ii)] $d(x, y) = d(y, x);$ 
  \item[iii)] $d(x, z) \leq d(x, y) + d(y, z).$
\end{itemize}

\begin{def*}
  A basis $\mathcal{B}$ for a topology is a collection of subsets of X such that
 \begin{itemize}
   \item[i)] For each x in X, there is at least one B in $\mathcal{B}$ containing x;
   \item[ii)] If x belongs to the intersection of two basis elements, there is a basis element containing x and inside their intersection.
 \end{itemize}
\end{def*}

Another characterization of a basis is as follows:
\begin{theo*}
  Let X be a topological space. Suppose that $\mathcal{C}$ is a collection of open sets of X such that for each open set
U and each x in U, there is an element C of $\mathcal{C}$ such that $x\in{C}\subseteq{U}$. Then, C is a basis for the topology 
of X.
\end{theo*}

For a product of topological spaces, we can define a topology on it based on the topologies of each individual space as follows:
\begin{def*}
  Let X = $\prod\limits _{\alpha\in{J}} X _{\alpha}$, where each $X _{\alpha}$ is a topological space. We define the product
topology on X as the one given by the basis $\mathcal{B}$ such that each basis element is defined as
  $$
  B = \prod _{\alpha\in{J}} U _{\alpha}, \quad U _{\alpha}\neq{X _{\alpha}} \text{ for all but finitely many }\alpha
  $$
\end{def*}

Each metric defines a topology themselves, known as the metric topology, in which basis elements are open balls and
the topology is induced by this basis.
\begin{def*}
  Given a metric space (X, d), an open ball of radius $\epsilon$ centered at a is the set
  $$
  B_d(a, \epsilon) := \{x\in{X}: d(x, a) < \epsilon\}.
  $$
\end{def*}
\begin{def*}
  Given a metric space (X, d), the metric topology $\tau_d$ induced by d on X is the one generated by the basis
 $\mathcal{B}$ whose basis elements are open balls.
\end{def*}

\section{Day 24/11/2022}
\subsection{Introduction and Main Set}
The main goal of these seminar (/notes) is to prepare whoever is using them to understand sequence spaces and their
construction, with the final goal of reaching the Cantor Set construction. We start off defining our main set,
known as the Sequence Space of N-1 digits, i.e., 
 \begin{align*}
   &\Omega_{N} := \{\omega = (\cdots, \omega _{-1}, \omega _{0}, \omega _{1}, \cdots): \omega _{i}\in \{0, 1, \cdots, N-1\}\} = \{0, 1, \cdots, N-1\}^{\mathbb{Z}} \\
   &\Omega _{N}^{R} := \{\omega = (\omega _{0}, \cdots): \omega _{i}\in \{0, 1, \cdots, N-1\}\} = \{0, 1, \cdots, N-1\} ^{\mathbb{N}}
 \end{align*}
One way to think of this family of spaces is that it records the results from an infinite game of throwing N-sided dices.
For instance, if we stay simple and assume a game of heads-and-tails, with only two possibilities, the space would be
 \begin{align*}
 \Omega _{2}^{R} = \{0, 1\} ^{\mathbb{N}} = \{\omega = (\omega _{0}, \cdots): \omega _{i}\in \{0, 1\}\}
 \end{align*}
This space specifically is the one we are going to work the most with, since it is going to be
shown that it is equivalent to a Cantor Set, and it also makes for an easy example regarding whatever
new construction we add to the space.

\subsection{Structuring the Space}
  The next few steps are related to the structure of this space. We're going to define a topology on it, followed 
by a metric. Start by endowing $\{0, 1, \cdots, N-1\}$ with the discrete topology, in a way that
since the space is finite, it is also compact. From here, consider the sets $X _{i} = \{0, 1, \cdots, 
N-1\}, i\in \mathbb{N}$, and define
  $$
    B = \prod\limits_{i=1}^{n-1}U _{i} \times{} \prod\limits_{i=n}^{\infty}X _{i},
  $$ 
where each $U _{i}$ is a proper subset of $X _{i}$. Hence, the collection $\mathcal{B}$ of all the sets
B form a basis for the product topology on $\Omega _{N}^{R}  $
  
For example, consider N = 2, i.e., the topology on $\{0, 1\}$, in which the discrete topology is $\tau = \{\emptyset, \{0, 1\}, \{0\}, \{1\}\}$. 
Then, the basis for the product topology is given by 
  $$
  B = \prod\limits_{i=1}^{n-1}U _{i} \times{} \prod\limits_{i=n}^{\infty}X _{i} = \prod\limits_{i=1}^{n}\{b_i\}\times{}\prod\limits_{i=n}^{\infty}U_i.
  $$ 
em que $b _{i}\in\{0, 1\}$ e $U _{i} = \{0, 1\} $. Another way of defining the topology is via what is known as cylinder sets, defined by fixing integers $n _{1} < \cdots < n _{k}$ and $\alpha _{1}, \cdots, 
\alpha _{k}\in \{0, 1, \cdots, N-1\} $, and putting
  $$
  C _{\alpha _{1}, \cdots, \alpha _{k}}^{n _{1}, \cdots, n _{k}}:= \{\omega\in \Omega _{N}^{R}: \omega _{n_i} = \alpha _{i}\}
  $$
where i varies from 1 to k. Specifically, this is known as a cylinder of rank k, and the topology to be defined is
such that all open sets are cylinders, hence the basis is given by them. However, to show that it is indeed a basis,
take $x\in{C _{\alpha _{1}, \cdots, \alpha _{k}}^{n _{1}, \cdots, n _{k}}}$. Hence, for some $1\leq{j}\leq{k}$,
  $$
  x\in C _{\alpha _{1}}^{n _{1}}\cap C _{\alpha _{2}}^{n _{2}} \cap \cdots \cap C _{\alpha _{k}}^{n _{k}}
  $$
so that it satisfies the theorem characterizing a basis, i.e., $\mathcal{C}$ is a basis of cylinders. Moreover,
notice that given a cylinder, 
  $$
  \Omega _{N}^{R}\SLash\{C_{\alpha_{1}, \cdots, \alpha_{k}}^{n_{1}, \cdots, n_{k}}\} = \{\omega\in \Omega_{N}^{R}: \omega_{n_{i}}\neq \alpha_{i}, i = 1, \cdots, k\} = C^{n_{1}, \cdots, n_{k}}_{\sigma(\alpha_{1}), \cdots, \sigma(\alpha_{k}),}
  $$
where $\sigma$ is a permutation that excludes the j-th term $(\sigma(\alpha_{i})\neq \alpha_{k}\forall i=1, \cdots, k).$ As a consequence,
we see that every cylinder is both open and closed in $\Omega_{N}^{R}.$

  Our next step will be defining a metric for our space and prove some of its properties.
\newpage

\section{Day 05/12/2022}
\subsection{Motivations}
\begin{itemize}
  \item Cylinders are clopen sets;
  \item Sequence space metric;
  \item Cylinders are open balls in that metric;
  \item $\Omega_{N}$ is a perfect set (First part of showing the homeomorphism with a Cantor Set).
\end{itemize}
\subsection{Reviewing}
  Topics from last class:
 \begin{itemize}
   \item Introduced the main space we're working on;
   \item Defined the bases for the topology on $\Omega_{N}^{R}$;
   \item We showed that each cylinder set form open sets.
 \end{itemize}
 \subsection{$\Omega_{N}^{R}$ as a Metric Space}
  Our goal with this is to define a metric such that the space is perfect and can be related to the cylinder topology.
For a fixed $\lambda > 1,$ define $d:\Omega_{N}^{R}\times{\Omega_{N}^{R}}\rightarrow \mathbb{R}$ by
  $$
    d_{\lambda}(\omega, \omega') = \sum\limits_{n=-\infty}^{\infty} \frac{|\omega_{n} - \omega_{n}'|}{\lambda^{|n|}}.
  $$
  Checking the metric axioms is not the point of this seminar, thus it's left undone on the notes. However, it hurts no one to 
comment that it all follows from the properties granted from the usual metric of $\mathbb{R}^{n}$ (i.e. the absolute value).

\subsection{Open Balls in $\Omega_{N}^{R}$}
  Using the definition of open balls (c.f. Section 1)k, let's analyze the case of an open ball centered at 0 with raidus r
with the metric we just defined. For the sake of simplicity, take N to be 2, so that for large $\lambda$, specifically $\lambda=10N=20$, fix
the zero sequence $\omega' = (\cdots, 0, 0, 0, \cdots)$. We want to find $r > 0$ such that $B_{r}(\omega') = C_{0}^{0} = \{\nu = (\nu_{n})_{n\in\mathbb{Z}}: \nu_{0} = 0\}.$
Equivalently, we're going to prove that
  $$
  \{\omega\in  \Omega_{2}: d_{\lambda}(\omega, \omega') < r\} = \{\omega\in \Omega_{2}: \omega_{0} = 0\}.
  $$
  Analyzing the terms of the series under these condition, one gets 
  $$
  d_{\lambda}(\omega, \omega') = \sum\limits_{n=-\infty}^{\infty} \frac{|\omega_{n} - \omega_{n}'|}{\lambda^{|n|}} = \sum\limits_{n=-\infty}^{\infty} \frac{|\omega_{n}|}{20^{|n|}}
  $$
It helps to visualize a few cases of n to understand the behavior of the series. In fact, it follows that
  \begin{align*}
  &n=0 \rightarrow \frac{|\omega_{0} - \omega_{0}'|}{20^{n}} = \left\{\begin{array}{ll}
      0, \quad \text{if } \omega_{0} = \omega_{0}' = 0 \\
      \frac{1}{1} = 1, \quad \text{if } \omega_{0}\neq \omega_{0}'
    \end{array}\right.\\
  &n=1 \rightarrow \frac{|\omega_{1} - \omega_{1}'|}{20} = \left\{\begin{array}{ll}
        0, \quad \text{if } \omega_{1} = \omega_{1}' = 0 \\
        \frac{1}{20}, \quad \text{if } \omega_{1}\neq \omega_{1}'
      \end{array}\right.\\
  &  \vdots\\
  &n=k \rightarrow \frac{|\omega_{\pm k} - \omega_{\pm k}'|}{20^{|k|}} = \left\{\begin{array}{ll}
      0, \quad \text{if } \omega_{\pm k} = \omega_{\pm k}' \\
      \frac{1}{20^{|k|}}, \quad \text{if } \omega_{\pm k}\neq \omega_{\pm k}
    \end{array}\right.
  \end{align*}
  In other words, we are looking for an r such that
  $$
    d_{\lambda}(\omega, \omega') = \left\{\begin{array}{ll}
        \sum\limits_{n=-\infty}^{\infty}\frac{1}{20^{|n|}}, \quad \omega_{n}\neq \omega_{n} \\
        0, \quad \omega_{n} = \omega_{n}'
      \end{array}\right.
  $$
  Because $\displaystyle \frac{1}{20} < 1,$ this series converges, so that it works for any $r\in\biggl(\sum\limits_{|n|\geq{1}}^{}20^{-n}, 1\biggr]$ works.
In fact, the cases in which $\omega_{n} = \omega_{n}'$ for some $n\in \mathbb{Z}$ yield
  $$
    d(\omega, \omega')\leq \sum\limits_{|n|\geq{1}}^{}20^{-n} < r
  $$
Notice that the case r = 1 must be included if $\omega_{0}\neq \omega_{0}'$ but $\omega_{n} = \omega_{n}'$ for $n\in \mathbb{Z}\SLash \{ 0\} $. 
Moreover, notice that $20^{-n}$ is just $\lambda^{-n}$, such that we can calculate the radius of the ball for a given large $\lambda.$

  One final comment should be added. On any metric space, a topology given by the metric itself can be created by setting
the basis to be open balls and open sets being their union. That way, the topology induced by the metric just studied, in which
open balls have been shown to be cylinders, is one generated by them (cylinders). Hence, it is equivalent to the first topology we
defined on $\Omega_{N}^{R}!$
\newpage

\section{Day 12/12/2022}
\subsection{Reviewing}
Topics from last class:
  \begin{itemize}
    \item Showed that cylinders form open sets and are equivalent to open balls with the metric:
  $$
  d_{\lambda}(\omega, \omega') = \sum_{n=-\infty}^{\infty}\frac{|\omega _{n} - \omega' _{n}|}{\lambda ^{|n|}};
  $$
  \item Found a connection between product topology and metric topology;
  \item Showed that cylinders are clopen sets;
  \item Showed that the metric above has less contributions from higher order terms.
  \end{itemize}
\subsection{Connectedness}
On today's seminar, we are going to see a few topological concepts needed to better grasp the ideas behind
the relationship between Cantor Sets and Sequence Spaces. Starting with the notion of connectedness of a space,
the intuition behind is that of a "space that is a single piece." Formally, we define it as
\begin{def*}
  If X is a set such that it cannot be divided into two disjoint non-empty open sets, then X is connected.
\end{def*}
For our purposes, even though this definition given is the most intuitive, we are going to use an equivalent 
definition, namely 
 \begin{def*}
   A space X is connected when the only two sets that are both open and closed are X and $\emptyset.$
 \end{def*}
 The usefulness comes from the fact that since our Cylinder sets are clopen, just like it was proved on the last
seminar, there is no connected subspace of X other than one-point sets, which are trivially connected. Thus the 
space is totally disconnected. Hence, we've cooked one ingredient in our Cantor Set homeomorphism soup.

\subsection{Perfect Set}
To cut it short, 
\begin{def*}
  A set X is said to be perfect if it is closed and has no isolated point.
\end{def*}
However, we must clarify what is an isolated point. We define an element x of X to be an isolated point provided
that there exists a neighborhood U of x that contains no other points besides x itself. In other words,
a point is not an isolated points if every neighborhood U of x contains at least one more point p other than x.

Now, recall from calculus and analysis the definition of a limit point:
\begin{quote}
  ``An element x of a set S is said to be a limit point if every neighorhood U of x contains at least one point
  p such that $p\neq{x}.$"  
\end{quote}
We conclude that a set X is perfect provided that it is closed AND every point of X is a limit point! 

Let's show that $\Omega _{2} ^{R}$ is a perfect set, i.e., we are going to prove that given a point $\omega\in\Omega _{2}^{R}$,
then $\omega\in{C _{\alpha_i}^{n_i}}.$ However, notice that whichever other $\omega'\in\Omega$ whose i-th entry is also
$\alpha_i$ also belongs to that neighborhood of $\omega$. Hence, the same reasoning shows that any neighborhood of
$\omega$ contains other points different from it. Thus, since our point was arbitrary, this is true for any element
of $\Omega _{2}^{R}$, showing that any point is a limit point. We conclude from this that our space is perfect.
\newpage

\section{Seminar Day 30/03/2023}
\subsection{Motivations}
\begin{itemize}
  \item Review Topology;
  \item Construct the $\sigma$-algebra that will be used;
  \item Construct the Middle-Third Cantor set via sequences of functions randomly picked.
\end{itemize}
\subsection{The Motivation Problem}
  As Kevin talked about last week, we can construct the Cantor Middle-Third set through a function known as the Hutchinson Attractor, denoted by B, ranging
from the set $\mathcal{H}(M)$ of nonempty compact subsets of a metric space M to $\mathcal{H}(M)$ itself and given by the union of the images of 
contractions in M. The way we construct it is, for instance, by applying B to a singleton set A = $\{x\}$ and using de previously defined metric $d_{H}$ to translate
the result to the Cantor Set. For each n iterations, we get an ammount of parts of the CMT set equal to $2^{n}.$ 
Now consider two functions $f_{i}:[0,1]\rightarrow [0, 1]$
  $$
    f_{i} = \left\{\begin{array}{ll}
        \frac{x}{3}, \quad i=0\\
        \frac{x}{3}+\frac{2}{3}, \quad i=1\\
      \end{array}\right.
  $$
  The infinite application of these functions yield the Cantor set, which shall be denoted by $\mathcal{C}$ to make things easier. In other words,
Consider now a representation of infinitely many combinations of 0's and 1's in any order, i.e., $\omega = (0, 1, 0, 0, 1, \cdots)$ and
let $f_{\omega}^{n}$ be the repeated use of $f_{i}$ as defined before using the indices from $\omega$, so that
  $$
  f_{\omega}^{n}(x) = f_{\omega_{n-1}}\circ{\cdots}\circ{f_{\omega_{1}}}\circ{f_{\omega_{0}}}(x)
  $$
  indicates that we start using the n-th coordinate of $\omega$ on each f. Using the example of $\omega$ from before, $f_{\omega}^{n}$
  would be
  $$
    f_{\omega}^{n}(x) = f_{\omega_{n-1}}\circ{\cdots}\circ{f_{0}}\circ{f_{1}}\circ{f_{0}}(x).
  $$
  Using that notation, the thesis given at the start that the infinite use of $f_{i}$ eventually covers all of $\mathcal{C}$ is the same as
  $$
  \lim_{l\to\infty}\overline{\{f_{\omega}^{n}(x):n\geq{l}\}} = B
  $$
  That begs the question: Will EVERY sequence of digits $\omega\in\{0, 1\}^{\mathbb{N}}$, when combined with $f_{i}$, give 
as its image the Cantor set? In fact, the answer is no, as the theorem is stated
 \begin{theo*}
   Let $\phi$ be an independent and identically distributed random product of contractions $f_{1},\cdots, f_{k}:M\rightarrow M$ and
  K be the corresponding Hutchinson Attractor. Given $p\in M$, we have
    $$
    \lim_{l\to\infty}\overline{\{f_{\omega}^{n}:n\geq{l}\}} = K
    $$
    for $\mathbb{P}-$almost all $\omega.$
 \end{theo*}
On that note, to grasp what we mean by almost all sequences work, consider a sequence of a single digit, i.e., $\omega =\{0, 0, 0, \cdots\} $. Then, when we apply this to $f_{i}$, we get
  \begin{align*}
    f_{\omega}^{n}(x) &= f_{0}\circ{\cdots}f_{0}\circ{f_{0}}\circ{f_{0}}(x)\\
                      &= f_{0}\circ{\cdots}f_{0}(\frac{x}{3}) \\
                      &= f_{0}\circ{\cdots}f_{0}(\frac{x}{9}) \\
                      &\vdots\\
                      &= \frac{x}{3^{n}}.
  \end{align*}
  Because of this, as n goes to infinity, $f_{\omega}^{n}$ tends to 0, which is not the Cantor set. In other words,
  $$
    \lim_{l\to\infty}\overline{\{f_{\omega}^{n}(x):n\geq{l}\}}\neq B.
  $$
  a new problem arises, that is, will the number of $\omega$'s for which the initial thesis hold be way too small to be relevant? The answer is going to need
quite a bit of measure theory, for the answer is, in fact, that the result holds for almost every $\omega$.

\subsection{The Meaning of ``Almost Every''}
  Now that the goal has been set, we can start to develop the theory needed to fully grasp it. Starting with a review of $\sigma-$algebra,
they are the sets in which we define measures. They are sets that have closure under countable unions and complements. Formally speaking,
 \begin{def*}
   Given a set $\Omega$, a $\sigma-$algebra $\mathcal{F}$ is a nonempty collection of subsets of $\Omega$ that satisfy
  \begin{align*}
    &(i) \text{ If }A\in \mathcal{F} \Rightarrow A^{c}\in \mathcal{F};\\
    &(ii) \text{ If } A_{i} \text{ is a countable sequence of sets, then } \bigcup_{i}A_{i}\in \mathcal{F};\\
    &(iii) \Omega\in \mathcal{F}.\square
  \end{align*}
 \end{def*}
 They are the defining ground that allow us to define measures and thus, find the meaning of ``Almost Every''. Without further ado,
we define a measure.
 \begin{def*}
   A measure is a nonnegative countably additive set function, i.e., a function $\mu:\mathcal{F}\rightarrow \mathbb{R}$ which satisfies
  \begin{itemize}
    \item[i)] $\mu(A)\geq{\mu(\emptyset)}=0$ for all $A\in \mathcal{F};$ 
    \item[ii)] If $A_{i}\in \mathcal{F}$ is a countable sequence of disjoint sets, then
      $$
        \mu(\bigcup_{i}A_{i}) = \sum\limits_{i}^{}\mu(A_{i}).\square
      $$
  \end{itemize}
 \end{def*}
 Now, we can formalize the meaning of almost every point satisfying something. The idea is that some property is going to hold true
for every point of a set except for an ammount inside a set whose significance is nought. In other words, a set with a measure of zero, so that
the set for which the property holds takes up nearly every single possibility. 
 \begin{def*}
   Given a measure space $(\Omega, \mathcal{F}, \mu)$, in which $\Omega$ is a set, $\mathcal{F}$ is a $\sigma-$algebra, and $\mu$ is a measure, 
 a property P is said to hold almost everywhere if there exists a set $N\in\Sigma$ with $\mu(N) = 0,$ and all $x\in\Omega/N$ satisfy that property.
 \end{def*}
  It's also important to understand what it means for a variable to be independent and identically distributed, since it allows
for simplifications of results and ideas. Essentially, it means that the an element in the sequence of variables 
does not depend on the ones that came before it, and the value does not change with each subsequent application of it.
The easiest example of such kinds of elements come up in the toss of coins, since the result of ``head'' or ``tail''
has no impact on the next tossing of coin, and neither does the probability change from 0.5 each time you flip it,
meaning it is identically distributed. However, we need a mathematical definition to work better with it.
\begin{def*}
  Suppose random variables X and Y are defined to assume values in $I\subseteq{\mathbb{R}}$. Let $F_{X}(x) = P(X\leq{x}), 
F_{Y}(y) = P(Y\leq{y})$ denote the cumulative distribution function of X and Y. Furthermore, denote their joint cumulative
distributive function by
  $$
    F_{X, Y}(x, y) = P(X\leq{x}\wedge Y\leq{y}).
  $$
\end{def*}
 \begin{def*}
   Two random variables X and Y are independent if and only if
   $$
    F_{X}(x) = F_{Y}(x)\quad \forall x\in I\subseteq{\mathbb{R}}.
   $$
   Moreover, they are said to be identically distributed if and only if 
   $$
    F_{X, Y}(x, y)=F_{X}(x)F_{Y}(y)\quad \forall x, y\in I\subseteq{\mathbb{R}}.
   $$
   When both happen, we say that they are i.i.d.
 \end{def*}
  The thing is that we don't work with only two variables (usually). Thankfully, we do have a definition for multiple variables
 \begin{def*}
   We say that n random variables $X_{1},\cdots,X_{n}$ are independent if and only if 
   $$
   F_{X_{1}}(x) = F_{X_{k}}(x)\quad \forall k\in\{1,\cdots,n\}\text{ and }\forall x\in I
   $$
   On the other hand, they are identically distributed if and only if 
   $$
    F_{X_{1},\cdots,X_{n}}(x) = F_{X_{1}}(x_{1})\cdots F_{X_{n}}(x_{n})\quad \forall x_{1},\cdots,x_{n}\in I
   $$
 where $F_{X_{1},\cdots,X_{n}}(x_{1},\cdots,x_{n})=P(X_{1}\leq{x_{1}}\wedge\cdots\wedge X_{n}\leq{x_{n}})$ denotes the joint 
  cumulative distribution function of $X_{1},\cdots,X_{n}.\square$
 \end{def*}


\subsection{The Topology of Cylinder Sets and Sequence Spaces}
 Regarding the topology of cylinder sets, 
 \begin{def*}
  Fix integers $n _{1} < \cdots < n _{k}$ and $\alpha _{1}, \cdots, \alpha _{k}\in \{0, 1, \cdots, N-1\} $. Then, the cylinder of rank k is the set
  $$
  C _{\alpha _{1}, \cdots, \alpha _{k}}^{n _{1}, \cdots, n _{k}}:= \{\omega\in \Omega _{N}^{R}: \omega _{n_i} = \alpha _{i}\}
  $$
where i varies from 1 to k. Another notation that may be used is 
  $$
    [\alpha_{0}, \cdots, \alpha_{k}] = C_{\alpha_{1},\cdots,\alpha_{k}}^{n_{1},\cdots,n_{k}}.
  $$
 \end{def*}
 The elements of cylinders are exactly the k first coordinates of an element $\omega\in \{0, 1\}^{\mathbb{N}},$ and it should
be noted that we may not know the other coordinates other than those k first ones. Cylinders are both open and closed 
sets simultaneously, as can be shown. The elements we are going to use as part of the definition of f will be members of
the cylinders.
  
  Furthermore, we endow the space $\{0, 1\}^{\mathbb{N}}$ with the smallest topology that makes projections continuous functions, the product topology,
which has a subbasis formed exactly by the preimage of projections and a basis of cylinders. 
\begin{def*}
  Let X = $\prod\limits _{\alpha\in{J}} X _{\alpha}$, where each $X _{\alpha}$ is a topological space. We define the product
topology on X as the one given by the basis $\mathcal{B}$ such that each basis element is defined as
  $$
  B = \prod _{\alpha\in{J}} U _{\alpha}, \quad U _{\alpha}\neq{X _{\alpha}} \text{ for all but finitely many }\alpha
  $$
\end{def*}
  The product topology in question has as reference the discrete topology on $\{0, 1\}$
 
\end{document}

